\mytitile\\~

### 2020-01-30 document.tex
Brackets and BMSTU corrections

% ****** Start of file aipsamp.tex ****m*
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 pra,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{fixme}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{hyperref}
\usepackage{kbordermatrix}% http://www.hss.caltech.edu/~kcb/TeX/kbordermatrix.sty
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{xparse}
\usepackage{bbm}
\usepackage{xcolor}

@@

\newcommand{\mytitile}{Light-dressing of a 
diatomic supercondufcing artificial molecule}

@@

	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}
	\affiliation{
		National University of Science and Technology MISIS, Moscow, Russia
	}%
	\author{V.B. Yursa}
	\affiliation{ 
		Skolkovo Institute of Science and 
		Technology, Moscow, Russian Federation
	}%

@@

	\author{A.A. Pischimova}
	\affiliation{FMN Laboratory, Bauman Moscow 
	State Technical University, Moscow, Russia}
	\affiliation{Dukhov Automatics Research 
	Institute, (VNIIA), Moscow, Russia}

	\author{O.V. Astafiev}
	\affiliation{Skolkovo Institute of Science 
		and Technology, Moscow, Russian Federation}
	\affiliation{
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia}
	\affiliation{Physics Department, Royal 
	Holloway, University of London, Egham, Surrey 
	TW20 0EX, United Kingdom}
\affiliation{National Physical Laboratory, Teddington, TW11 0LW, United Kingdom}
%

@@

	\begin{abstract}
	In this work, we irradiate a superconducting 
	artificial molecule composed of two 
	magnetic-flux-tunable transmons with 
	microwave light while monitoring its state 
	via joint dispersive readout. At certain 
	fluxes, the molecule demonstrates a complex 
	spectrum deviating qualitatively from the 
	solution of the Schrödinger equation without 
	driving. We reproduce the observed extra 
	spectral lines accurately by numerical 
	simulations, and find them to be a 
	consequence of an Autler-Townes-like effect 
	when a single tone is simultaneously dressing 
	the system and probing the transitions 
	between new eigenstates. We present 
	self-consistent analytical models accounting 
	both these processes at the same time that 
	agree well with both experiment and numerical 
	simulation. This study is an important step 
	towards understanding the behaviour of complex
	systems of many atoms interacting	with strong radiation.
	\end{abstract}

@@

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws\cite{you2011atomic,Qopt_1300refs}. Their Hamiltonians can be pre-designed
and engineered which makes them a particularly 
versatile tool for studies in quantum optics, and high controllability of their parameters
allows direct observation of novel physical 
effects previously inaccessible for natural 
systems.

One of the most prominent milestones that 
superconducting quantum circuits have reached so 
far is the strong coupling with light in {circuit 
QED}\cite{wallraff2004strong, 
chiorescu2004coherent} when the relaxation and decoherence rates
appear smaller than the Rabi frequency. 
Currently, they are surpassing all other 
implementations of strong coupling in terms of 
coherence\cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and 
molecules, SAAs do not even require confined 
radiation to implement strong coupling with 
light: they may be coupled unprecedently strongly 
to free-propagating electromagnetic waves in 1D 
on-chip waveguides\cite{astafiev2010resonance} 
without using cavities at all. The Rabi frequency 
in this case may reach 50\% of the transition 
frequency\cite{deng2015observation} which is even 
beyond strong coupling 
regime\cite{forn2019ultrastrong}. To correctly 
describe the behaviour of an atom in these 
conditions, the so-called \textit{dressed atom 
approach}\cite{cohen1998atom} is employed when 
the radiation has to be directly included in the 
Hamiltonian and affects its level structure.

So far, experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics  were
focused on single artificial 
atoms\cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes (A-T) splittings of
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs\cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of similar composite structures with intense driving field. While there were studies on dressing
of multi-atomic systems in a 
cavity\cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with external dressing field is not less attractive since its
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule\cite{kou2017fluxonium} (SAM). We use two 
Xmon-type\cite{barends2013coherent} 
transmons\cite{koch2007charge} interacting with 
each other through a cavity 
bus\cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar antenna while its state can be
monitored by joint dispersive readout using the 
same coupling cavity\cite{chow2010detecting}. We 
find that strong interaction with microwaves not 
only results in multiphoton transitions of
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules\cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We note that there 
were no such experiments with natural molecules, 
which could in principle demonstrate same 
effects, because they lack controllability and 
coherence of superconducting quantum devices, and 
previous studies of SAAs under strong driving field
either involved just a single atom or have 
demonstrated only the standard spectral 
signatures known from the quantum optics (see 
Appendix \ref{sec:3-level-at}).

Besides its fundamental importance, this 
experiment may be useful for future quantum 
computers: a quantum engineer should account for 
the observed behaviours carefully controlling the 
driving power (for instance, as we will show, the 
bSWAP gate\cite{poletto2012entanglement} is 
directly affected by light dressing).

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs\cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J,
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled
to a single notch-type\cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples\cite{majer2007coupling} the transmons and 
allows joint readout \cite{chow2010detecting} of
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown, where the layout of the components is presented. The
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw''\cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in color on the sides; their SQUIDs are
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

@@

A single transmon SAA can be regarded as an 
oscillator with a quartic perturbation describing 
the leading-order anharmonicity. Therefore, in 
the main text we do not use the charge and phase 
operators and write down its Hamiltonian using 
only the annihilation operator $\hat b$:
\begin{equation}
\hat{{H}}_{tr}/\hbar = \omega \hat 
b^{\dagger}\hat b +\frac{1}{2}\alpha \hat 
b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\label{eq:h1tr}
\end{equation}
where $\omega$ is its 
$\ket{0}\rightarrow\ket{1}$, or fundamental, 
transition frequency and $\alpha$ is the 
anharmonicity of the transmon. By applying 
magnetic flux to the transmon's SQUID (either via 
an individual on-chip line or via an external 
coil) it is possible\cite{koch2007charge} to 
directly  control $\omega$. In our modelling, we 
take into account the three lowest states of the 
transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).

@@

Next, we assemble the model for two coupled 
transmons with the corresponding annihilation 
operators $\hat b$ and $\hat c$, the fundamental 
frequencies $\omega_{1,2}$ and anharmonicities 
$\alpha_{1,2}$. The corresponding Hamiltonian of 
the SAM contains two terms representing each 
transmon, two terms representing the interaction 
of each transmon with the driving field at the 
same frequency $\omega_d$, and the 
transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat 
b^\dag)(\hat c+\hat c^{\dagger})$ is the 
transverse interaction between the atoms. 
Strictly speaking, $J = J(\omega_1, \omega_2)$ 
depends on the transmon 
frequencies\cite{koch2007charge}, but we take $J$ 
to be a constant as in \autoref{tab:parameters} 
due to its negligible variation for our range of 
frequencies.

@@

In the following, we will also transform 
\autoref{Hsystem} into the frame rotating with 
both drives by an operator
\begin{equation}
\hat R = \exp[-i t (\omega_d^1 
b^{\dagger}b+\omega_d^2 
c^{\dagger}c)],\label{eq:R}
\end{equation}
arriving at
\begin{equation}
\hat H_R = \hat R^{\dagger}\hat H \hat R -	 
{i}\hat R^{\dagger}\partial_t \hat 
R.\label{eq:rotation}
\end{equation}
Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow \hbar J \left[\hat 
	b^\dag \hat c e^{it(\omega_d^1 - \omega_d^2)} 
	+ \hat b \hat c^\dag e^{-it(\omega_d^1 - 
	\omega_d^2)}\right],\\
	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

Besides the unitary evolution, we take into 
account the incoherent processes of relaxation 
and dephasing for each transmon. They are 
modelled using the Lindblad equation with the 
following collapse 
operators\cite{bishop2010circuit}:
\begin{equation}\
\begin{split}
\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, 
\hat b^\dag \hat b,\\
\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, 
\hat c^\dag \hat c,
\end{split}
\end{equation}
where $\gamma_{1,2}$ are the individual 
relaxation rates, and $\gamma_{\phi (1,2)}$ are 
the pure dephasing rates. As one can see, the 
collapse operators are in a separable form, i.e. 
acting only upon a single transmon each. This is 
a valid approach until the coupling strength $J$ 
is not too large\cite{beaudoin2011dissipation}. 
Therefore, the complete evolution equation for 
the system density matrix $\hat \rho$ is
\begin{equation}
\partial_t \hat \rho_{(R)} = \frac{i}{\hbar}[\hat 
\rho, \hat H_{(R)}] + \sum_{\alpha, i} 
\mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho_{(R)} 
= \mathcal{L}\hat\rho_{(R)}, \label{eq:master}
\end{equation}
where $\mathcal{D}[\hat{{O}}]\hat \rho = 
\hat{{O}} \hat \rho \hat{{O}}^\dag - 
\frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat 
\rho\}$ and $\mathcal{L}$ is the Liouville 
superoperator, or the Liouvillian; $_{(R)}$ 
denotes if the Hamiltonian and the corresponding 
solution density matrix are in the rotating frame 
with RWA. In this work, we do not alter the 
dissipator terms when changing the reference 
frame despite that it may not be correct in 
general\cite{shavit2019bridging}.

The readout resonator is not included in the 
model since in the dispersive regime it does not 
affect the dynamics of the SAM. Hence, the 
readout is modelled just by some measurement 
operator $\hat M(f_p)$ that can be obtained by 
finding the transmission $S_{21}(f_p)$ ($f_p$ is 
the probe frequency near the resonance) through 
the sample after preparing various states of the 
SAM. Another way to find $\hat M(f_p)$ is to 
calculate $S_{21}(f_p)$ via offsetting the 
experimental resonance curve measured when the 
SAM is in the ground state by the dispersive 
shifts corresponding to the SAM basis 
states\cite{filipp2009two, chow2010detecting}. Since we have not
directly measured these dispersive shifts, in our 
modelling they are treated as fitting parameters. 
Finally, the observable value for any state $\hat 
\rho$ is calculated as $S_{21}^{sim}(f_p) = 
\Tr[\hat M(f_p) \hat \rho]$.

@@

Numerical simulations are necessary for studying 
\autoref{eq:master} since is does not have an 
analytical solution. We have been using the 
\textit{qutip}\cite{johansson2013qutip} (quantum 
optics toolbox in Python) to simulate the 
dynamics and to find the steady state of the 
system for various parameter combinations of the 
Liouvillian.

Two distinct modes of simulation were used in the 
modelling. The first one is for the Liouvillians 
that do not explicitly depend on time. In this 
case, the steady state $\hat \rho_{ss}$ of the 
system should be calculated from the set of 
linear equations obtained from \autoref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} 
\hat \rho = 0
\label{eq:steady}
\end{equation}
This equation is solved with the qutip's 
\textit{steadystate} 
function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}.
 This method is applicable when the driving 
frequency for both transmons is the same because 
from \autoref{eq:RWA} follows that $\hat H_{int}$ 
is time independent when $\omega_d^1 = 
\omega_d^2$.

>>>>

% ****** Start of file aipsamp.tex ****m*
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 aps, prx,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
superscriptaddress
]{revtex4-2}

\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{fixme}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{hyperref}
\usepackage{kbordermatrix}% http://www.hss.caltech.edu/~kcb/TeX/kbordermatrix.sty
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{xparse}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{url}

@@

\newcommand{\mytitile}{Light-dressing of a 
diatomic superconducting artificial molecule}

@@

	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}
	\affiliation{
		National University of Science and Technology MISIS, Moscow, Russia
	}%
	\author{V.B. Yursa}
	\affiliation{Skolkovo Institute of Science 
		and Technology, Moscow, Russian Federation}%

@@

	\author{A.A. Pishchimova}
	\affiliation{FMN Laboratory, Bauman Moscow 
	State Technical University, Moscow, Russia}
	\affiliation{Dukhov Automatics Research 
	Institute, (VNIIA), Moscow, Russia}

	\author{O.V. Astafiev}
	\affiliation{Skolkovo Institute of Science 
		and Technology, Moscow, Russian Federation}
	\affiliation{ 
		Moscow Institute of Physics and Technology, 
		Dolgoprundiy, Russia
	}
	\affiliation{Physics Department, Royal 
	Holloway, University of London, Egham, Surrey 
	TW20 0EX, United Kingdom}
\affiliation{National Physical Laboratory, Teddington, TW11 0LW, United Kingdom}
%

@@

	\begin{abstract}
	In this work, we irradiate a superconducting 
	artificial molecule composed of two 
	magnetic-flux-tunable transmons with 
	microwave light while monitoring its state 
	via joint dispersive readout. At certain 
	fluxes, the molecule demonstrates a complex 
	spectrum deviating qualitatively from the 
	solution of the Schrödinger equation without 
	driving. We reproduce the observed extra 
	spectral lines accurately by numerical 
	simulations, and find them to be a 
	consequence of an Autler-Townes-like effect 
	when a single tone is simultaneously dressing 
	the system and probing the transitions 
	between new eigenstates. We present 
	self-consistent analytical models accounting 
	both these processes at the same time that 
	agree well with both experiment and numerical 
	simulation. This study is an important step 
	towards understanding the behaviour of complex
	systems of many atoms interacting coherently with strong radiation.
	\end{abstract}

@@

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws \cite{you2011atomic,Qopt_1300refs}. Their Hamiltonians can be pre-designed 
and engineered which makes them a particularly 
versatile tool for studies in quantum optics, and high controllability of their parameters 
allows direct observation of novel physical effects previously inaccessible for natural 
systems.

One of the most prominent milestones that 
superconducting quantum circuits have reached so 
far is the strong coupling with light in {circuit 
QED} \cite{wallraff2004strong, 
chiorescu2004coherent} when the relaxation and decoherence rates 
appear smaller than the Rabi frequency. 
Currently, they are surpassing all other 
implementations of strong coupling in terms of 
coherence \cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and 
molecules, SAAs do not even require confined 
radiation to implement strong coupling with 
light: they may be coupled unprecedently strongly 
to free-propagating electromagnetic waves in 1D 
on-chip waveguides \cite{astafiev2010resonance} 
without using cavities at all. The Rabi frequency 
in this case may reach 50\% of the transition 
frequency \cite{deng2015observation} which is even 
beyond strong coupling 
regime \cite{forn2019ultrastrong}. To correctly 
describe the behaviour of an atom in these 
conditions, the so-called \textit{dressed atom 
approach} \cite{cohen1998atom} is employed when 
the radiation has to be directly included in the 
Hamiltonian and affects its level structure.

So far, experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics  were 
focused on single artificial 
atoms \cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes (A-T) splittings of 
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs \cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of similar composite structures with intense driving field. While there were studies on dressing 
of multi-atomic systems in a 
cavity \cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with external dressing field is not less attractive since its 
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule \cite{kou2017fluxonium} (SAM). We use two 
Xmon-type \cite{barends2013coherent} 
transmons \cite{koch2007charge} interacting with 
each other through a cavity 
bus \cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar antenna while its state can be 
monitored by joint dispersive readout using the 
same coupling cavity \cite{chow2010detecting}. We 
find that strong interaction with microwaves not 
only results in multiphoton transitions of 
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules \cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We note that there 
were no such experiments with natural molecules, 
which could in principle demonstrate same 
effects, because they lack controllability and 
coherence of superconducting quantum devices, and 
previous studies of SAAs under strong driving field 
either involved just a single atom or have 
demonstrated only the standard spectral 
signatures known from the quantum optics (see 
Appendix \ref{sec:3-level-at}).

Besides its fundamental importance, this 
experiment may be useful for future quantum 
computers: a quantum engineer should account for 
the observed behaviours carefully controlling the 
driving power (for instance, as we will show, the 
bSWAP gate \cite{poletto2012entanglement} is 
directly affected by light dressing).

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs \cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J, 
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled 
to a single notch-type \cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples \cite{majer2007coupling} the transmons and 
allows joint readout  \cite{chow2010detecting} of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown, where the layout of the components is presented. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw'' \cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in color on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

@@

A single transmon SAA can be regarded as an 
oscillator with a quartic perturbation describing 
the leading-order anharmonicity. Therefore, in 
the main text we do not use the charge and phase 
operators and write down its Hamiltonian using 
only the annihilation operator $\hat b$:
\begin{equation}
\hat{{H}}_{tr}/\hbar = \omega \hat 
b^{\dagger}\hat b +\frac{1}{2}\alpha \hat 
b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\label{eq:h1tr}
\end{equation}
where $\omega$ is its 
$\ket{0}\rightarrow\ket{1}$, or fundamental, 
transition frequency and $\alpha$ is the 
anharmonicity of the transmon. By applying 
magnetic flux to the transmon's SQUID (either via 
an individual on-chip line or via an external 
coil) it is possible \cite{koch2007charge} to 
directly  control $\omega$. In our modelling, we 
take into account the three lowest states of the 
transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).

@@

Next, we assemble the model for two coupled 
transmons with the corresponding annihilation 
operators $\hat b$ and $\hat c$, the fundamental 
frequencies $\omega_{1,2}$ and anharmonicities 
$\alpha_{1,2}$. The corresponding Hamiltonian of 
the SAM contains two terms representing each 
transmon, two terms representing the interaction 
of each transmon with the driving field at the 
same frequency $\omega_d$, and the 
transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat 
b^\dag)(\hat c+\hat c^{\dagger})$ is the 
transverse interaction between the atoms. 
Strictly speaking, $J = J(\omega_1, \omega_2)$ 
depends on the transmon 
frequencies \cite{koch2007charge}, but we take $J$ 
to be a constant as in \autoref{tab:parameters} 
due to its negligible variation for our range of 
frequencies.

@@

In the following, we will also transform 
\autoref{Hsystem} into the frame rotating with 
both drives by an operator
\begin{equation}
\hat R = \exp[-i t (\omega_d^1 
b^{\dagger}b+\omega_d^2 
c^{\dagger}c)],\label{eq:R}
\end{equation}
arriving at
\begin{equation}
\hat H_R = \hat R^{\dagger}\hat H \hat R -	 
{i}\hat R^{\dagger}\partial_t \hat 
R.\label{eq:rotation}
\end{equation}
Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
\begin{equation}
\begin{aligned}
	\omega_{\{1,2\}} &\rightarrow \Delta_{\{1,2\}} = \omega_{\{1,2\}} - \omega_d^{\{1,2\}},\\
	\hat H_{int} &\rightarrow \hbar J \left[\hat 
	b^\dag \hat c e^{it(\omega_d^1 - \omega_d^2)} 
	+ \hat b \hat c^\dag e^{-it(\omega_d^1 - 
	\omega_d^2)}\right],\\
	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

Besides the unitary evolution, we take into 
account the incoherent processes of relaxation 
and dephasing for each transmon. They are 
modelled using the Lindblad equation with the 
following collapse 
operators \cite{bishop2010circuit}:
\begin{equation}\
\begin{split}
\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, 
\hat b^\dag \hat b,\\
\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, 
\hat c^\dag \hat c,
\end{split}
\end{equation}
where $\gamma_{1,2}$ are the individual 
relaxation rates, and $\gamma_{\phi (1,2)}$ are 
the pure dephasing rates. As one can see, the 
collapse operators are in a separable form, i.e. 
acting only upon a single transmon each. This is 
a valid approach until the coupling strength $J$ 
is not too large \cite{beaudoin2011dissipation}. 
Therefore, the complete evolution equation for 
the system density matrix $\hat \rho$ is
\begin{equation}
\partial_t \hat \rho_{(R)} = \frac{i}{\hbar}[\hat 
\rho, \hat H_{(R)}] + \sum_{\alpha, i} 
\mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho_{(R)} 
= \mathcal{L}\hat\rho_{(R)}, \label{eq:master}
\end{equation}
where $\mathcal{D}[\hat{{O}}]\hat \rho = 
\hat{{O}} \hat \rho \hat{{O}}^\dag - 
\frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat 
\rho\}$ and $\mathcal{L}$ is the Liouville 
superoperator, or the Liouvillian; $_{(R)}$ 
denotes if the Hamiltonian and the corresponding 
solution density matrix are in the rotating frame 
with RWA. In this work, we do not alter the 
dissipator terms when changing the reference 
frame despite that it may not be correct in 
general \cite{shavit2019bridging}.

The readout resonator is not included in the 
model since in the dispersive regime it does not 
affect the dynamics of the SAM. Hence, the 
readout is modelled just by some measurement 
operator $\hat M(f_p)$ that can be obtained by 
finding the transmission $S_{21}(f_p)$ ($f_p$ is 
the probe frequency near the resonance) through 
the sample after preparing various states of the 
SAM. Another way to find $\hat M(f_p)$ is to 
calculate $S_{21}(f_p)$ via offsetting the 
experimental resonance curve measured when the 
SAM is in the ground state by the dispersive 
shifts corresponding to the SAM basis 
states \cite{filipp2009two, chow2010detecting}. Since we have not 
directly measured these dispersive shifts, in our 
modelling they are treated as fitting parameters. 
Finally, the observable value for any state $\hat 
\rho$ is calculated as $S_{21}^{sim}(f_p) = 
\Tr[\hat M(f_p) \hat \rho]$.

@@

Numerical simulations are necessary for studying 
\autoref{eq:master} since is does not have an 
analytical solution. We have been using the 
\textit{qutip} \cite{johansson2013qutip} (quantum 
optics toolbox in Python) to simulate the 
dynamics and to find the steady state of the 
system for various parameter combinations of the 
Liouvillian. The source code for the simulations can be found on GitHub \footnote{\url{https://github.com/vdrhtc/Examples/tree/master/transmon-simulations/two_transmons}}.

Two distinct modes of simulation were used in the 
modelling. The first one is for the Liouvillians 
that do not explicitly depend on time. In this 
case, the steady state $\hat \rho_{ss}$ of the 
system should be calculated from the set of 
linear equations obtained from \autoref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} 
\hat \rho = 0
\label{eq:steady}
\end{equation}
This equation is solved with the qutip's 
\textit{steadystate} 
function \footnote{\url{http://qutip.org/docs/4.0.2/guide/guide-steady.html}}.
 This method is applicable when the driving 
frequency for both transmons is the same because 
from \autoref{eq:RWA} follows that $\hat H_{int}$ 
is time independent when $\omega_d^1 = 
\omega_d^2$.
